```{r setup, include = FALSE}
library(foreign)
library(dplyr)

options(scipen = 10)

# note I should probably be using the wfw.dat file, but the way it's been coded
# is incomprehensible, so I'm going to model with heights.dta instead
earnings <- read.dta("~/projects/arm/ARM_Data/earnings/heights.dta")

```

```{r a}
earnings <- earnings %>%
  select(earn, sex, height) %>%
  filter(!is.na(earn) 
         & !is.na(height))

```

```{r b}
m1 <- lm(earn ~ height, data = earnings)

earnings$height_z <- with(earnings, (height - mean(height)) / sd(height))

m2 <- lm(earn ~ height_z, data = earnings)

```

The average height is `r round(mean(earnings$height))`, so we expect, a person with that height to earn `r round(coef(m2)[[1]])`, on average.

```{r c}
# this model doesn't work because there are earnings of 0
# m3 <- lm(log(earn) ~ height, data = earnings)

m4 <- lm(log(earn + 10e-6) ~ height, data = earnings)

# adding sex gives a nice bump to R-squared
m5 <- lm(earn ~ height + sex, data = earnings)

m6 <- lm(earn ~ height + sex + height:sex, data = earnings)

m7 <- lm(earn ~ height_z + sex + height_z:sex, data = earnings)

m8 <- lm(log(earn + 10e-6) ~ height_z + sex + height_z:sex, data = earnings)

```

Because it has the highest R-squared and the most interpretable coefficients, my preferred model is:

```{r m7}
summary(m7)

```

*Intercept*: The model suggests that the average predicted salary for a man with average height is `r round(coef(m7)[[1]])`.

*height_z*: The coefficient for the standardized height is `r round(coef(m7))[[2]]`, the expected difference in earnings for men for every 1 standard-deviation (`r round(sd(earnings$height), 2)`) increase in height.

*sex*: The coefficient for sex is `r round(coef(m7))[[3]]`, the expected difference in earnings for women compared to men of the same height.

*height_z:sex*: The coefficient for the interaction between standardized height and sex is `r round(coef(m7))[[4]]`, the difference in slopes between the predictive differences in height for men and women.
