```{r setup, include = FALSE}
library(foreign)
library(ggplot2)
library(dplyr)
library(tidyr)

iq_data <- read.dta("~/projects/arm/ARM_Data/child.iq/child.iq.dta")

```

```{r a}
m1 <- lm(ppvt ~ momage, data = iq_data)
summary(iq_data)
summary(m1)

ggplot(iq_data, aes(x = momage, y = ppvt)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE)

iq_data %>%
  mutate(residuals = residuals(m1)) %>%
  ggplot(aes(x = ppvt, y = residuals)) +
  geom_point() +
  geom_hline(yintercept = summary(m1)$sigma, color = "darkgray", linetype = 2) +
  geom_hline(yintercept = -summary(m1)$sigma, color = "darkgray", linetype = 2)

```

The pattern in the residuals suggests there's variation in the data not well explained by the model.

The slope coefficient of `momage` indicates that for every additional year of a mother's age, the average child's test score increases by 0.84.

This suggests mothers should give birth late in life, though that assumes that there's no negative effect brought on by childbirth in later age. (Note that in the data, `momage` stops at 29, so we don't have visibility into this.)

```{r b}
m2 <- lm(ppvt ~ momage + educ_cat, data = iq_data)
summary(m2)

gather(iq_data, predictor, x, educ_cat:momage) %>%
  ggplot(aes(x = x, y = ppvt, color = predictor)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  facet_grid(~ predictor, scales = "free_x")

iq_data %>%
  mutate(residuals = residuals(m2)) %>%
  gather(predictor, x, educ_cat:momage) %>%
  ggplot(aes(x = x, y = residuals, color = predictor)) +
  geom_point() +
  geom_hline(yintercept = summary(m2)$sigma, color = "darkgray", linetype = 2) +
  geom_hline(yintercept = -summary(m2)$sigma, color = "darkgray", linetype = 2) +
  facet_grid(~ predictor, scales = "free_x")

```

With mother's age held constant, an increase of 1 in a mother's education corresponds to an increase of 4.7 in an average child's test score (with standard error of 1.3).

With mother's education held constant, an increase of 1 in a mother's age corresponds to an increase of only 0.3 in an average child's test score (with standard error of 0.4).

When including mother's education in the model, the impact of mother's age seems much more negligible.

```{r c}
iq_data$high_school <- ifelse(iq_data$educ_cat > 1, 1, 0)

m3 <- lm(ppvt ~ momage + high_school:momage, data = iq_data)

summary(m3)

iq_data$colors <- ifelse(iq_data$high_school == 1, "black", "gray")

plot(iq_data$momage, iq_data$ppvt, col = iq_data$colors, pch = 20)
curve(cbind(1, 1, x) %*% coef(m3), add = TRUE, col = "black")
curve(cbind(1, 0, x) %*% coef(m3), add = TRUE, col = "gray")

```

The coefficient on the interaction between `momage` and `high_school` is 0.5, with a standard error of 0.1. This represents the difference in the slope of the mother's age for children whose mothers did and did not complete high school.

```{r d}
m4 <- lm(ppvt ~ momage + educ_cat, data = iq_data[1:200, ])
predicted <- predict(m4, iq_data[201:400, ])

data.frame(actual = iq_data[1:200, "ppvt"], predicted) %>%
  ggplot(aes(x = predicted, y = actual)) +
  geom_point() +
  scale_x_continuous(limits = c(30, 140)) +
  scale_y_continuous(limits = c(30, 140))

```
